|

### 2020-02-07 02-Chp2-Systematic-Review.Rmd
Updates

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
Hold
```
(ref:darwin-quote) --- Charles Darwin [@chang2012a]

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
Hold
```
(ref:darwin-quote) --- Charles Darwin [@chang2012]

### 2020-02-07 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Updates

This is a test of the bibliography\textsuperscript{{\textbf{???}}}

@@

\begin{savequote}
Hold
\qauthor{--- Charles Darwin\textsuperscript{{\textbf{???}}}}\end{savequote}

@@

Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{1}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{2}}
Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
Full-text screening will also be completed in full by the primary author. A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage will be recorded. Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{3}}

@@

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{4}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.

@@

Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{5}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{6}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bramer2016}{}%
1. Bramer, W. M., Giustini, D., de Jonge, G. B., Holland, L. \& Bekhuis, T. De-duplication of database search results for systematic reviews in EndNote. \emph{Journal of the Medical Library Association : JMLA} \textbf{104}, 240--243 (2016).

\leavevmode\hypertarget{ref-ouzzani2016}{}%
2. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).

\leavevmode\hypertarget{ref-zotero-766}{}%
3. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.

\leavevmode\hypertarget{ref-petersen1999}{}%
4. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).

\leavevmode\hypertarget{ref-sterne2019}{}%
5. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).

\leavevmode\hypertarget{ref-sterne2016}{}%
6. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).

>>>>

This is a test of the bibliography\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}

@@

\begin{savequote}
Hold
\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}

@@

Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{2}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{3}}
Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
Full-text screening will also be completed in full by the primary author. A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage will be recorded. Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{4}}

@@

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{5}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.

@@

Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{6}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{7}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-chang2012}{}%
1. Chang, C.-C. H., Zhao, Y., Lee, C.-W. \& Ganguli, M. Smoking, death, and Alzheimer's disease: A case of competing risks. \emph{Alzheimer Disease and Associated Disorders} \textbf{26}, 300--306 (2012).

\leavevmode\hypertarget{ref-bramer2016}{}%
2. Bramer, W. M., Giustini, D., de Jonge, G. B., Holland, L. \& Bekhuis, T. De-duplication of database search results for systematic reviews in EndNote. \emph{Journal of the Medical Library Association : JMLA} \textbf{104}, 240--243 (2016).

\leavevmode\hypertarget{ref-ouzzani2016}{}%
3. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).

\leavevmode\hypertarget{ref-zotero-766}{}%
4. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.

\leavevmode\hypertarget{ref-petersen1999}{}%
5. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).

\leavevmode\hypertarget{ref-sterne2019}{}%
6. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).

\leavevmode\hypertarget{ref-sterne2016}{}%
7. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).

### 2020-02-07 index.Rmd
Updates

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: none  
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    toc: true   
link-citations: true
documentclass: book

>>>>

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: none  
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    split_bib: false
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    toc: true   
link-citations: true
documentclass: book
